Grupo Bimbo Inventory Demand \\Data Science Report

### 2024-07-16 src/data-science-project/data_science_project/docs/paper/paper.tex
Orthography

        \item Data Transformation:
        \begin{itemize}
                \item Normalization and Scaling: Numerical features were normalized and scaled to ensure all features contribute equally to the model. StandardScaler from sklearn was used to transform features to have zero mean and unit variance.
        \end{itemize}

>>>>

        \item Data Transformation:
        \begin{itemize}
                \item Change type data: The columns were optimized by changing the data type (for example, going from int64 to int8)
        \end{itemize}

### 2024-07-16 src/data-science-project/data_science_project/docs/report/report.tex
Orthography

\section{Feature Engineering}
Feature engineering involved creating new variables to capture additional information and improve model performance.
\begin{itemize}
    \item Temporal Features: Lagged variables were created to capture temporal dependencies in sales and demand.
    \item Economic Indicators: The bi-weekly inflation rate and consumer confidence index were added as features to capture the impact of economic conditions on product demand.
    \item Categorical Encoding: Categorical variables were converted to numerical format using one-hot encoding or label encoding.

>>>>

\section{Feature Engineering}
Feature engineering involved creating new variables to capture additional information and improve model performance; and all characteristics were chosen except for inflation.
\begin{itemize}
    \item Temporal Features: Lagged variables were created to capture temporal dependencies in sales and demand.
    \item Economic Indicators: The bi-weekly inflation rate and consumer confidence index were added as features to capture the impact of economic conditions on product demand.
